---
title: "Preliminary Analyses RRI Tool Kit"
author: "Juan C. Correa"
output:
  word_document: default
---

# Intro
This is a short preliminary analysis of the contents included in the sample of projects indexed by the *Responsible Research and Innovation* (RRI) toolkit. By employing web scraping techniques, we were able to retrieve a total of 1,414 documents from RRI, along with a brief document description, their titles, and the discipline they belong to. 

```{r, echo=FALSE}
setwd("~/Documents/PaperOtoFelipe/")
library(readxl)
LT <- read_excel("RawDataRRI.xlsx", sheet = "Raw LowerTags")
library(tidyr)
disciplines <- LT[1:47]
```


As the initial data base contained several disciplines with quite similar categories (e.g., agrobiotechnology, agriculture, plant biology, smart farming), we decided to merge these categories under a single name. The resulting merged categories were re-named as follows:

* Agro = agribiotechnology + agriculture + plant biology + smart farming + Food + Food, agriculture, forestry, water and bio-economy + plant biology + rural environment
* Business & Industry
* Civil Society & Organization
* Climate = climate action + climate adaptation strategies + climate crisis + Climate, environment, and resources
* Energy = Energy + energy transition + renewable energy
* Ethics = ai ethics + Ethics + ethics of ai + responsible technology + security
* Health = health care + health technology + Health, demography & wellbeing + patient engagement + vaccine hesitancy + vaccines
* Technologies = Artificial intelligence + Digital technologies + emerging technologies + robotics
* Education = Education Community + Science education
* Govern = Governance + policy design + public engagement

```{r, echo=FALSE}
library(dplyr)
# Agro = agribiotechnology + agriculture + plant biology + smart farming + Food + Food, agriculture, forestry, water and bio-economy + plant biology + rural environment
Agro <-  LT[c(1:2, 4, 5, 33, 45, 21, 22, 42)]
Agro <- Agro %>% mutate(sum = rowSums(.[3:9])) %>% mutate(agro = ifelse(sum >= 1, 1, 0))
Agro <- Agro[c(1,2,11)]
# Business & Industry
Business <- LT[c(1:2, 8)]
Business <- Business %>% mutate(sum = Business$`Business & Industry`*1) %>% mutate(busi = ifelse(sum >= 1, 1, 0))
Business <- Business[c(1,2,5)]
# Climate = climate action + climate adaptation strategies + climate crisis + Climate, environment, and resources
Climate <- LT[c(1:2, 10:13)]
Climate <- Climate %>% mutate(sum = rowSums(.[3:6])) %>% mutate(climate = ifelse(sum >= 1, 1, 0))
Climate <- Climate[c(1,2,8)]
# Energy = Energy + energy transition + renewable energy
Energy <- LT[c(1:2, 17, 18, 38)]
Energy <- Energy %>% mutate(sum = rowSums(.[3:5])) %>% mutate(energy = ifelse(sum >= 1, 1, 0))
Energy <- Energy[c(1,2,7)]
# Ethics = ai ethics + Ethics + ethics of ai + responsible technology + security
Ethics <- LT[c(1:2, 6, 19, 20, 40, 44)]
Ethics <- Ethics %>% mutate(sum = rowSums(.[3:7])) %>% mutate(ethics = ifelse(sum >= 1, 1, 0))
Ethics <- Ethics[c(1,2,9)]
# Health = health care + health technology + Health, demography & wellbeing + patient engagement + vaccine hesitancy + vaccines
Health <- LT[c(1:2, 27, 28, 29, 32, 46, 47)]
Health <- Health %>% mutate(sum = rowSums(.[3:8])) %>% mutate(health = ifelse(sum >= 1, 1, 0))
Health <- Health[c(1,2,10)]
# Policy-Makers == 1
PM <- LT[c(1:2, 35)]
PM <- PM %>% mutate(sum = PM$`Policy Makers`*1) %>% mutate(policy = ifelse(sum >= 1, 1, 0))
PM <- PM[c(1:2,5)]
# Technologies = Artificial intelligence + Digital technologies + emerging technologies + robotics
Technologies <- LT[c(1:2, 7, 14, 16, 41)]
Technologies <- Technologies %>% mutate(sum = rowSums(.[3:6])) %>% mutate(technologies = ifelse(sum >= 1, 1, 0))
Technologies <- Technologies[c(1,2,8)]
# Education = Education Community + Science education
Education <- LT[c(1:2, 15, 43)]
Education <- Education %>% mutate(sum = rowSums(.[3:4])) %>% mutate(education = ifelse(sum >= 1, 1, 0))
Education <- Education[c(1,2,6)]
# Govern = Governance + policy design + public engagement
Govern <- LT[c(1:2, 25, 34, 32)]
Govern <- Govern %>% mutate(sum = rowSums(.[3:5])) %>% mutate(govern = ifelse(sum >= 1, 1, 0))
Govern <- Govern[c(1,2,7)]
# Civil Society
CivSoc <- LT[c(1:2, 9)]
CivSoc <- CivSoc %>% mutate(sum = rowSums(.[3])) %>% mutate(civsoc = ifelse(sum >= 1, 1, 0))
CivSoc <- CivSoc[c(1,2,5)]
Disciplines <- list(Agro, Business, CivSoc, Climate, Education, Energy, Ethics, Govern, Health, PM, Technologies)
rm(list=setdiff(ls(), "Disciplines"))
Disciplines <- do.call(cbind.data.frame, Disciplines)
```

Now, we have a clean data set to use for further analyses.
```{r}
Disciplines <- Disciplines[c(3, 6,9,12,15,18,21,24,27, 30, 33)]
variable.names(Disciplines)
```
We start by estimating the mutual information between categorized documents as a first general analysis
```{r}
library(infotheo)
DIM <- mutinformation(Disciplines, method = "mm")
library(corrplot)
library(RColorBrewer)
whiteblack <- colorRampPalette(c("#FFFFFF", "#E5E5E5", "#F3F3F3", "#D8D8D8", "#B1B1B1", "#8A8A8A", "#5D5D5D", "#000000"))
corrplot(DIM, is.corr = FALSE, cl.lim=c(min(DIM), max(DIM)), method = "number", type = "lower", col=whiteblack(6), tl.col = "black")

```

